---
title: "CryptoPunks EDA"
author: "Tam Trinh"
date: '2022-05-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load Dataset and Setup

Import libraries
```{r}
library(dplyr)
library(ggplot2)
library(RColorBrewer)


```


Load dataset
```{r}

punk1 <- read.csv('punk_attribute_data/0-999.csv')
punk2 <- read.csv('punk_attribute_data/1000-1999.csv')
punk3 <- read.csv('punk_attribute_data/2000-2999.csv')
punk4 <- read.csv('punk_attribute_data/3000-3999.csv')
punk5 <- read.csv('punk_attribute_data/4000-4999.csv')
punk6 <- read.csv('punk_attribute_data/5000-5999.csv')
punk7 <- read.csv('punk_attribute_data/6000-6999.csv')
punk8 <- read.csv('punk_attribute_data/7000-7999.csv')
punk9 <- read.csv('punk_attribute_data/8000-8999.csv')
punk10 <- read.csv('punk_attribute_data/9000-9999.csv')

```


Combine dataframes into one
```{r}
AllPunk <- rbind(punk1, punk2, punk3, punk4, punk5, punk6, punk7, punk8, punk9, punk10)

```


Create df with CryptoPunk attributes and load data
```{r}
attr <- read.csv('punk_attribute_data/CryptoPunks Attributes - Accessories Type.csv', header=T, na.strings=c("","NA"))

```


# Wrangle Data

Slice smaller df to test
```{r}
punktest <- AllPunk[1:10, ]
```


Write function for finding attribute from string
```{r}
# The attributes of the CryptoPunks are listed in a string under "accessories" - I'd like to pull them out and put them under columns by accessory group

attr_func <- function(attr.col, target.string) {
  for (a in attr.col) {
    if (is.na(a) == FALSE) {
      if (grepl(a, target.string) == TRUE) {
        return(a)
      }
    }
}
}


attr_test <- attr_func(attr$Hair, punktest$accessories[1])

```


Get colnames
```{r}
attr_names <- colnames(attr)
attr_names
```


Create function to get Hair accessories
```{r}
# Create function that can pull out individual attributes and be used to apply to whole columns 


Hair_func <- function(target.string) {
  for (a in attr$Hair) {
    if (is.na(a) == FALSE) {
      if (grepl(a, target.string) == TRUE) {
        return(a)
      }
    } else {
      return(NA)
    }
  }
}



punktest$Hair <- sapply(punktest$accessories, Hair_func)
# test on small df punktest
```


Create function to get Eyes accessories
```{r}

Eyes_func <- function(target.string) {
  for (a in attr$Eyes) {
    if (is.na(a) == FALSE) {
      if (grepl(a, target.string) == TRUE) {
        return(a)
      }
    } else {
      return(NA)
    }
  }
}


punktest$Eyes <- sapply(punktest$accessories, Eyes_func)

```


Create function to get Facial.Hair accessories
```{r}

Facial.Hair_func <- function(target.string) {
  for (a in attr$Facial.Hair) {
    if (is.na(a) == FALSE) {
      if (grepl(a, target.string) == TRUE) {
        return(a)
      }
    } else {
      return(NA)
    }
  }
}


punktest$Facial.Hair <- sapply(punktest$accessories, Facial.Hair_func)
```


Create function to get Mouth.Prop accessories
```{r}

Mouth.Prop_func <- function(target.string) {
  for (a in attr$Mouth.Prop) {
    if (is.na(a) == FALSE) {
      if (grepl(a, target.string) == TRUE) {
        return(a)
      }
    } else {
      return(NA)
    }
  }
}


punktest$Mouth.Prop <- sapply(punktest$accessories, Mouth.Prop_func)
```


Create function to get Lips accessories
```{r}

Lips_func <- function(target.string) {
  for (a in attr$Lips) {
    if (is.na(a) == FALSE) {
      if (grepl(a, target.string) == TRUE) {
        return(a)
      }
    } else {
      return(NA)
    }
  }
}


punktest$Lips <- sapply(punktest$accessories, Lips_func)
```


Create function to get Neck accessories
```{r}

Neck_func <- function(target.string) {
  for (a in attr$Neck) {
    if (is.na(a) == FALSE) {
      if (grepl(a, target.string) == TRUE) {
        return(a)
      }
    } else {
      return(NA)
    }
  }
}



punktest$Neck <- sapply(punktest$accessories, Neck_func)
```


Create function to get Cheeks accessories
```{r}

Cheeks_func <- function(target.string) {
  for (a in attr$Cheeks) {
    if (is.na(a) == FALSE) {
      if (grepl(a, target.string) == TRUE) {
        return(a)
      }
    } else {
      return(NA)
    }
  }
}



punktest$Cheeks <- sapply(punktest$accessories, Cheeks_func)
```


Create function to get Teeth accessories
```{r}

Teeth_func <- function(target.string) {
  for (a in attr$Teeth) {
    if (is.na(a) == FALSE) {
      if (grepl(a, target.string) == TRUE) {
        return(a)
      }
    } else {
      return(NA)
    }
  }
}


punktest$Teeth <- sapply(punktest$accessories, Teeth_func)
```


Create function to get Nose accessories
```{r}

Nose_func <- function(target.string) {
  for (a in attr$Nose) {
    if (is.na(a) == FALSE) {
      if (grepl(a, target.string) == TRUE) {
        return(a)
      }
    } else {
      return(NA)
    }
  }
}



punktest$Nose <- sapply(punktest$accessories, Nose_func)
```


Create function to get Ears accessories
```{r}

Ears_func <- function(target.string) {
  for (a in attr$Ears) {
    if (is.na(a) == FALSE) {
      if (grepl(a, target.string) == TRUE) {
        return(a)
      }
    } else {
      return(NA)
    }
  }
}



punktest$Ears <- sapply(punktest$accessories, Ears_func)
```


Look at punktest dataset
```{r}

summary(punktest)

sum(is.na(punktest))

str(punktest)

# the functions seem to work and the attrributes are added as columns in punktest df
```


Inspect AllPunk df
```{r}
summary(AllPunk)

sum(is.na(AllPunk))

str(AllPunk)

```


```{r}
colnames(attr)
```

Get Hair accessories from the AllPunk df
```{r}
AllPunk$Hair <- sapply(AllPunk$accessories, Hair_func)
```


```{r}
# I noticed "NULL" values in the Hair column after sapplying the function,
# which didn't have a chance to happen in the test df, so I converted the NULL values to NA, and then changed the column from list back to char

# test on punktest first
punktest$accessories[10] <- "Frown / VR"
#str(punktest)
punktest$Hair[punktest$Hair == 'NULL'] <- NA
punktest$Hair <- unlist(punktest$Hair)

#apply to AllPunk
#str(AllPunk)
AllPunk$Hair[AllPunk$Hair == 'NULL'] <- NA
AllPunk$Hair <- unlist(AllPunk$Hair)

str(AllPunk) # worked! NULLS changed to NA and unlisted
```


Sapply the rest of the accessories functions to AllPunk df
```{r}

AllPunk$Eyes <- sapply(AllPunk$accessories, Eyes_func)
AllPunk$Facial.Hair <- sapply(AllPunk$accessories, Facial.Hair_func)
AllPunk$Mouth.Prop <- sapply(AllPunk$accessories, Mouth.Prop_func)
AllPunk$Lips <- sapply(AllPunk$accessories, Lips_func)

AllPunk$Neck <- sapply(AllPunk$accessories, Neck_func)
AllPunk$Cheeks <- sapply(AllPunk$accessories, Cheeks_func)
AllPunk$Teeth <- sapply(AllPunk$accessories, Teeth_func)
AllPunk$Nose <- sapply(AllPunk$accessories, Nose_func)
AllPunk$Ears <- sapply(AllPunk$accessories, Ears_func)


```


# Visualize Each Attribute


Create Barplot for Hair Attribute
```{r}

ggplot(data=AllPunk, aes(x=Hair)) + 
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplot(data=subset(AllPunk, !is.na(Hair)), aes(x=reorder(Hair, Hair, function(x)-length(x)))) + 
  geom_bar(aes(fill=Hair), show.legend = FALSE) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90, vjust = .5, hjust=1),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Hair Attributes", y = "Count", x = "Hair Attributes")


```

Create barplot for Eyes Attribute
```{r}

ggplot(data=subset(AllPunk, !is.na(Eyes)), aes(x=reorder(Eyes, Eyes, function(x)-length(x)))) + 
  geom_bar(aes(fill=Eyes), show.legend = FALSE) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90, vjust = .5, hjust=1),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Eyes Attributes", y = "Count", x = "Eyes Attributes")

```


Create barplot for Facial.Hair Attribute
```{r}

ggplot(data=subset(AllPunk, !is.na(Facial.Hair)), aes(x=reorder(Facial.Hair, Facial.Hair, function(x)-length(x)))) + 
  geom_bar(aes(fill=Facial.Hair), show.legend = FALSE) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90, vjust = .5, hjust=1),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Facial Hair Attributes", y = "Count", x = "Facial Hair Attributes")

```


Create barplot for Mouth.Prop Attribute
```{r}

ggplot(data=subset(AllPunk, !is.na(Mouth.Prop)), aes(x=reorder(Mouth.Prop, Mouth.Prop, function(x)-length(x)))) + 
  geom_bar(aes(fill=Mouth.Prop), show.legend = FALSE) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 0, vjust = .5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Mouth Prop Attributes", y = "Count", x = "Mouth Prop Attributes")

```


Create barplot for Lips Attribute
```{r}

ggplot(data=subset(AllPunk, !is.na(Lips)), aes(x=reorder(Lips, Lips, function(x)-length(x)))) + 
  geom_bar(aes(fill=Lips), show.legend = FALSE) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 0, vjust = .5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) +
  labs(title = "Count of Lips Attributes", y = "Count", x = "Lips Attributes")

```


Create barplot for Neck Attribute
```{r}

ggplot(data=subset(AllPunk, !is.na(Neck)), aes(x=reorder(Neck, Neck, function(x)-length(x)))) + 
  geom_bar(aes(fill=Neck), show.legend = FALSE)  +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 0, vjust = .5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Neck Attributes", y = "Count", x = "Neck Attributes")

```


Create barplot for Cheeks Attribute
```{r}

ggplot(data=subset(AllPunk, !is.na(Cheeks)), aes(x=reorder(Cheeks, Cheeks, function(x)-length(x)))) + 
  geom_bar(aes(fill=Cheeks), show.legend = FALSE) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 0, vjust = .5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Cheeks Attributes", y = "Count", x = "Cheeks Attributes")

```


Create barplot for Teeth Attribute
```{r}

ggplot(data=subset(AllPunk, !is.na(Teeth)), aes(x=reorder(Teeth, Teeth, function(x)-length(x)))) + 
  geom_bar(aes(fill=Teeth), show.legend = FALSE) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 0, vjust = .5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Teeth Attributes", y = "Count", x = "Teeth Attributes") +
  scale_fill_brewer(palette = "Dark2")


ggplot(data=AllPunk, aes(x=Teeth)) + 
  geom_bar(aes(color=Teeth), show.legend = FALSE) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 0, vjust = .5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Teeth Attributes", y = "Count", x = "Teeth Attributes") 
```


Create barplot for Nose Attribute
```{r}

ggplot(data=subset(AllPunk, !is.na(Nose)), aes(x=reorder(Nose, Nose, function(x)-length(x)))) + 
  geom_bar(aes(fill=Nose), show.legend = FALSE) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Nose Attributes", y = "Count", x = "Nose Attributes") + scale_fill_brewer(palette = "Pastel1")


ggplot(data=AllPunk, aes(x=Nose)) + 
  geom_bar(aes(color=Nose), show.legend = FALSE) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Nose Attributes", y = "Count", x = "Nose Attributes") + scale_fill_brewer(palette = "Pastel1")
```


Create barplot for Ears Attribute
```{r}

ggplot(data=subset(AllPunk, !is.na(Ears)), aes(x=reorder(Ears, Ears, function(x)-length(x)))) + 
  geom_bar(aes(fill=Ears), show.legend = FALSE) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Ears Attributes", y = "Count", x = "Ears Attributes") + scale_fill_brewer(palette = "PiYG")


ggplot(data=AllPunk, aes(x=Ears)) + 
  geom_bar(aes(color=Ears), show.legend = FALSE) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Ears Attributes", y = "Count", x = "Ears Attributes") + scale_fill_brewer(palette = "PiYG")

```


Barplot of Type
```{r}
ggplot(data=subset(AllPunk, !is.na(type)), aes(x=reorder(type, type, function(x)-length(x)))) + 
  geom_bar(aes(fill=type), show.legend = FALSE) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Type", y = "Count", x = "Type") + scale_fill_brewer(palette = "PiYG")


ggplot(data=AllPunk, aes(x=type)) + 
  geom_bar(aes(fill=type), show.legend = FALSE) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Type", y = "Count", x = "Type") + scale_fill_brewer(palette = "PiYG")
```


Barplot of gender
```{r}
ggplot(data=subset(AllPunk, !is.na(type)), aes(x=reorder(gender, gender, function(x)-length(x)))) + 
  geom_bar(aes(fill=gender), show.legend = FALSE) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Gender", y = "Count", x = "Gender") + scale_fill_brewer(palette = "Pastel1")


ggplot(data=AllPunk, aes(x=gender)) + 
  geom_bar(aes(fill=gender), show.legend = FALSE) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Count of Gender", y = "Count", x = "Gender") + scale_fill_brewer(palette = "Pastel1")
```























